\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2014-11-26 pkg/partykit/inst/mloss/letter_mloss3.tex
add URL
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@641 255f4249-2263-4417-b1ea-8498779e27a7

I uploaded a rebuttal letter for our manuscript
``\textbf{partykit}: A Modular Toolkit for Recursive Partytioning in R'' to the
Machine Learning Open-Source Software track of the Journal of Machine
Learning Research.

Referee 3 criticised the limited breath of our contribution and suggested to
copy the \texttt{cforest} function from package \emph{party} to package
\emph{partykit}, iterating an argument by Referee 2 from the previous
round. In the rebuttal letter, we explain the reason why it is currently not
helpful to move this function from one CRAN package to another one. In
addition, we took the liberty to discuss why we think that \emph{partykit}
is actually much more general than \emph{party} and, if one adopts a certain
point of view, also more general than most of the established machine
learning toolboxes. Since no changes in the manuscript were requested, we
did not touch the four page description.

Sincerely yours, \\
\includegraphics[width = .25\textwidth]{TH_Unterschrift}

>>>>

I uploaded a revised version of our manuscript
``\textbf{partykit}: A Modular Toolkit for Recursive Partytioning in R'' to the
Machine Learning Open-Source Software track of the Journal of Machine
Learning Research.

Reviewer~3 suggested to add forest functionality to the \emph{partykit}
package to increase it breadth.
This suggestion was already brought up in the previous revision by
Reviewer~2 and answered to the satisfaction of the first two reviewers:
While the basic idea for setting up a generic class for ``random forests''
is straightforward, many of the details in the implementation are not
obvious at all and deserve much more attention.  
Of course, we could easily copy the code of the old \texttt{party::cforest}
into the new \emph{partykit} package but this would not increase the
usefulness for the practitioner because \emph{party} is easily available. We
therefore decided not to follow the suggestion by reviewer~3 for the same
reasons as explained in the previous round and, in more detail now, the
rebuttal letter.

We revised the manuscript following the Instructions for Authors closely and
will send the copyright forms upon acceptance.

Best regards, \\
\includegraphics[width = .25\textwidth]{TH_Unterschrift}
